Hunting experience and prey variability jointly shape individual foraging specialisation in a predator-prey videogame

### 2022-10-10 manuscript/Chapter3-manuscript.Rmd
updated MS + word. added tables. first sketch.

library(data.table)
library(brms)

@@

We analyzed the predator's average speed and the average speed of the prey encountered by the predator. The predator's average speed is measured as the average distance per second traveled during a match (m/s) (mean = `r toString(format(round(mean(dat$pred_speed), digits = 2), nsmall = 2))`, sd = mean = `r toString(format(round(sd(dat$pred_speed), digits = 2), nsmall = 2))`). For the prey, we averaged the travel speed of the four individuals within a match to obtain the average speed of the group, also measured in meters per second (mean = `r toString(format(round(mean(dat$prey_avg_speed), digits = 2), nsmall = 2))`, sd = mean = `r toString(format(round(sd(dat$prey_avg_speed), digits = 2), nsmall = 2))`). Hunting success was defined as the number of prey consumed during the match (min = `r toString(format(round(min(dat$hunting_success)))`, max = `r toString(format(max(dat$hunting_success)))`). Lastly, the predator's cumulative experience was defined as the number of matches played prior to the match being monitored. For example, the first match of a player would have a cumulative experience value of 0, while the 10^th match would have a value of 9.

@@

```{r out.width = "100%", fig.cap = "**Figure 1.** Results from the Bayesian generalized linear mixed model. (A) Fitted (solid) line displaying the posterior predicted values relating the predators' hunting success to their cumulative experience. Here, we transformed the hunting success and cumulative experience back to their original scale (i.e. the amount of prey captured and the number of matches played respectively). The band around the solid line represents the 95% credible intervals. (B) The estimated posterior predicted mean hunting success of each predator player. We display the hunting success back-transformed to its original scale."}
knitr::include_graphics(here::here("outputs", "05_outputs_figures", "05_figure1.png"))
```

@@

```{r out.width = "100%", fig.cap = "**Figure 2.** Coefficient of variation for the predator's speed and for the speed of the prey encountered at each level of experience. (A) Coefficient of variation for the among individual differences in average behavior. (B) Coefficient fo variation for the among individual differences in within individual variance (i.e. specialization)."}
knitr::include_graphics(here::here("outputs", "05_outputs_figures", "05_figure2.png"))
```

@@

```{r out.width = "100%", fig.cap = "**Figure 3.** Title (A) Novice. (B) Advanced."}
knitr::include_graphics(here::here("outputs", "05_outputs_figures", "05_figure3.png"))
```

@@

```{r out.width = "100%", fig.cap = "**Figure 4.** Title (A) and (B) Novice. (C) and (D) Advanced."}
knitr::include_graphics(here::here("outputs", "05_outputs_figures", "05_figure4.png"))
```

>>>>

library(data.table)
library(brms)
library(flextable)
library(officer)

@@

We analyzed the predator's average speed and the average speed of the prey encountered by the predator. The predator's average speed is measured as the average distance per second traveled during a match (m/s) (mean = `r toString(format(round(mean(dat$pred_speed), digits = 2), nsmall = 2))`, sd = mean = `r toString(format(round(sd(dat$pred_speed), digits = 2), nsmall = 2))`). For the prey, we averaged the travel speed of the four individuals within a match to obtain the average speed of the group, also measured in meters per second (mean = `r toString(format(round(mean(dat$prey_avg_speed), digits = 2), nsmall = 2))`, sd = mean = `r toString(format(round(sd(dat$prey_avg_speed), digits = 2), nsmall = 2))`). Hunting success was defined as the number of prey consumed during the match (min = `r toString(format(min(dat$hunting_success)))`, max = `r toString(format(max(dat$hunting_success)))`). Lastly, the predator's cumulative experience was defined as the number of matches played prior to the match being monitored. For example, the first match of a player would have a cumulative experience value of 0, while the 10^th match would have a value of 9.

@@

```{r, ft.align = "left"}

tab1 <- readRDS(here::here("outputs", "05_outputs_tables", "05_table1.rds"))

set_caption(
  tab1,
  caption = "LOO table",
  style = "Table Caption"
)

<br>

blablabla

```{r, ft.align = "left"}

tab2 <- readRDS(here::here("outputs", "05_outputs_tables", "05_table2.rds"))

set_caption(
  tab2,
  caption = "Posterior mean values, standard errors, and 95% credible intervals for the GAMM with a common global smoother",
  style = "Table Caption"
)

@@

```{r out.width = "100%", fig.cap = "**Figure 2.** Coefficient of variation for the predator's speed and for the speed of the prey encountered at each level of experience. (A) Coefficient of variation for the among individual differences in average behavior. (B) Coefficient fo variation for the among individual differences in within individual variance (i.e. specialization)."}

knitr::include_graphics(here::here("outputs", "05_outputs_figures", "05_figure2.png"))

@@

```{r out.width = "100%", fig.cap = "**Figure 3.** Title (A) Novice. (B) Advanced."}

knitr::include_graphics(here::here("outputs", "05_outputs_figures", "05_figure3.png"))

@@

```{r out.width = "100%", fig.cap = "**Figure 4.** Title (A) and (B) Novice. (C) and (D) Advanced."}

knitr::include_graphics(here::here("outputs", "05_outputs_figures", "05_figure4.png"))
